---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# oipa: An R Interface to the Openaid International Aid Transparency Initiative Parser and API

The [International Aid Transparency Initiatives (IATI)](https://iatistandard.org/) is a global aid transparency standard and it makes information about aid spending easier to access, use and understand using a unified open standard. [Openaid IATI Parser and Application Programming Interface (OIPA)](https://www.oipa.nl/) enables IATI standard compliant dadtasets to easily parse and interface that data using API that has been developed on the Django framework. This package provides an R interface to the OIPA.

## Installation

You can install oipa from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("validmeasures/oipa")
```

